Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2021-02-04 05_calibration_data.Rmd
more style

pal <- RColorBrewer::brewer.pal(5, "Set1")
pal[3] = "seagreen"
pal[2] = RColorBrewer::brewer.pal(5, "Blues")[5]
```

@@

```{r echo=FALSE}
# plot filtered data
fig_speed_outliers <-
  ggplot() +
  geom_point(
    data = data,
    aes(x, y,
      col = speed_in < 25.6
    ),
    size = 0.3, alpha = 0.5,
    show.legend = F
  ) +
  annotate(
    geom = "rect",
    xmin = 650785, xmax = 653250,
    ymin = 5904450, ymax = 5906133,
    fill = NA, col = "grey20"
  ) +
  annotate(
    geom = "rect",
    ymin = 5901650, ymax = 5903100,
    xmin = 650000, xmax = 650600,
    fill = NA, col = "grey20"
  ) +
  scale_color_manual(values = c("grey", pal[3])) +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  )+
  ggspatial::annotation_scale(location = "tl") +
  coord_sf(crs = 32631)
# save
ggsave(fig_speed_outliers,
  filename = "figures/fig_speed_outlier.png",
  width = 170 / 25, height = 170 / 25
)
```

>>>>

pal <- RColorBrewer::brewer.pal(5, "Set1")
pal[3] <- "seagreen"
pal[2] <- RColorBrewer::brewer.pal(5, "Blues")[5]
```

@@

```{r echo=FALSE}
# plot filtered data
fig_speed_outliers <-
  ggplot() +
  geom_point(
    data = data,
    aes(x, y,
      col = speed_in < 25.6
    ),
    size = 0.3, alpha = 0.5,
    show.legend = F
  ) +
  annotate(
    geom = "rect",
    xmin = 650785, xmax = 653250,
    ymin = 5904450, ymax = 5906133,
    fill = NA, col = "grey20"
  ) +
  annotate(
    geom = "rect",
    ymin = 5901650, ymax = 5903100,
    xmin = 650000, xmax = 650600,
    fill = NA, col = "grey20"
  ) +
  scale_color_manual(values = c("grey", pal[3])) +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  ggspatial::annotation_scale(location = "tl") +
  coord_sf(crs = 32631)
# save
ggsave(fig_speed_outliers,
  filename = "figures/fig_speed_outlier.png",
  width = 170 / 25, height = 170 / 25
)
```
